\chapter{Feedback Surveys}
\label{appf:survey}

At various times during the design and iteration of VCWiz, we solicited feedback from founders and investors. This appendix documents the questions that were asked, and the set of answers permitted, when applicable.

\section{VCWiz Founder Survey}
\label{appf:survey:founders}

\begin{enumerate}
  \item How likely are you to recommend VCWiz to a friend?
    \subitem \textit{The founder was presented with a scale from 0 to 10}
  \item Have you used VCWiz?
    \subitem No
    \subitem Yes, I used it for my fundraise!
    \subitem Yes, I used it to research investors
    \subitem Yes, I clicked around a bit
    \subitem Yes, I used it to fill out my investor profile
    \subitem Other \textit{(free-form)}
  \item What's preventing you from using VCWiz more often?
    \subitem No
    \subitem Yes, I used it for my fundraise!
    \subitem Yes, I used it to research investors
    \subitem Yes, I clicked around a bit
    \subitem Yes, I used it to fill out my investor profile
    \subitem Other \textit{(free-form)}
  \item VCWiz has an intro request functionality, that helps you get connected to investors. Have you tried this out?
    \subitem Yes
    \subitem I didn't know I could do that
    \subitem It didn't work when I tried
    \subitem I couldn't figure out how to use it
    \subitem I don't need any intros right now
    \subitem I prefer to get my intros warm
    \subitem Other \textit{(free-form)}
  \item VCWiz also has a feature called Link, which scans your inbox and syncs your VCWiz dashboard with ongoing conversations with investors. Have you tried this out?
    \subitem Yes
    \subitem No, because I have privacy concerns
    \subitem No, because I don't need it
    \subitem No, because I use a different CRM
    \subitem No, because I don't know how to enable it
    \subitem Other \textit{(free-form)}
  \item Any other feedback for us? What's your \#1 feature request?
    \subitem \textit{The founder was presented with a free-form response box}
\end{enumerate}

\section{VCWiz Investor Survey}
\label{appf:survey:investors}

\begin{enumerate}
  \item Why did you end up not engaging with the founder(s) that reached out to you?
    \subitem I didn't see the intro request email
    \subitem I didn't know what it was, so I ignored it
    \subitem I was annoyed about receiving the email
    \subitem I didn't have time to look at the email
    \subitem I don't respond to cold emails
    \subitem Other \textit{(free-form)}
\end{enumerate}

\section{VCWiz User Testing}
\label{appf:survey:users}

All of the following questions were presented with boxes for free-form text responses, unless otherwise specified.

\begin{enumerate}
  \item What's your name?
  \item Were you able to test out VCWiz?
    \subitem Yes
    \subitem No
  \item What went wrong?
  \item What did you like about the product?
  \item What did you dislike?
  \item How do you discover new investors currently? What are your biggest complains with this process?
  \item What tools have you used for discovering investors in the past?
  \item How do you organize your outreach to new investors currently? What are your biggest complains with this process?
  \item What tools have you used for organizing your outreach to investors in the past?
  \item Have you used dedicated software for managing investor relationships?
    \subitem Yes
    \subitem No
  \item What have your biggest complaints been with those tools?
  \item What has prevented you from using dedicated tools?
  \item Would you use VCWiz as it exists today?
    \subitem Yes
    \subitem No
  \item What would have to change for you to use VCWiz?
  \item How likely are you to recommend VCWiz to a fellow founder?
    \subitem \textit{The founder was presented with a scale from 1 to 5}
  \item What is the one most important feature to add to VCWiz?
  \item Anything else we should know?
\end{enumerate}

\clearpage
\newpage
