\chapter{Introduction}

In this thesis, we aim to elucidate the founder-investor matching process, as experienced by early-stage venture funds and the startup founders they invest in. We do this by exploring the creation of a tool, VCWiz, and a study on the data generated from this tool. The tool's goal is to capture existing best-practices in order to bring more efficiency and equitability to the matching process, while collecting data that allows for a further quantitative analysis. VCWiz was built collaboratively with input from best-in-class founders and investors, and is currently used by thousands of founders actively. Data from this tool lead to the creation of the VCWiz Email Graph, a social-professional graph of founders, investors, and their intermediaries with edges based on frequency of emails between addresses. This data is used to examine how the fundraising process compares to commonly-accepted expectations. It is also used in our presentation of FounderRank, a methodology for ranking a founder's ability to fundraise based on their position in their social graph.

We begin in Chapter \ref{ch:ch2} by defining and detailing the inner workings of venture capital investments, and our chosen models of the behaviors of both founders and investors. We explore the opportunities in venture capital to leverage software, and justify the selection of VCWiz, a comprehensive fundraising tool for seed-stage founders, incorporating discovery, research, and outreach functionality. Chapter \ref{ch:ch3} documents the design, implementation, and launch of VCWiz. We document and analyze feedback gathered from founders across the spectrum of experience at various iterations of the tool. This feedback allows us to draw conclusions about the way founders use tools during fundraising, and how systems can be built to service those use cases. Chapter \ref{ch:ch4} presents a final VCWiz product: the end result of months of iteration and feedback. Following this, Chapter \ref{ch:ch5} details a study which explores the data generated by founders on VCWiz. This study aims to discover the significance of social characteristics when fundraising. We explore how investors can rank a set of founders based on these characteristics, and what attributes of a founder set him or her up well to raise money from venture capitalists.

\section{Goals}

The goal of this thesis is to learn more about the process of matching founders to investors. To do this, we will attempt to improve the existing process, and draw conclusions from the outcomes of this attempt. Improving the process entails making that process more efficient, in terms of the number and quality of successful matches that occur, but also more equitable, by combating the latent biases found in venture capital today with equal access to information.

For founders, our attempt to improve the process involves creating a tool which better equips a founder with the background knowledge, interfaces, and access necessary to find the right investors for their company. For investors, we aim to describe what exactly it means to find successful founder in the context of fundraising. We want to show how existing information can be used to determine the likelihood of a founder's fundraising success, and how to better rank inbound investment opportunities as a result. We strive to create a tool and study which help both sides of the venture capital transaction achieve efficiency, without enforcing existing biases and stereotypes.

Specifically, our goals are to: determine the state of the tools and processes used for founder-investor matching today, build and evaluate a tool which helps founders match with their optimal investors, and use the data from the tool to educate both founders and investors on efficient matching.

\section{A Tool}

VCWiz is a comprehensive tool for seed-stage startup founders to raise their first round of financing. It is a holistic tool which covers discovering relevant venture firms, researching firms and investors of interest, and managing a structured outreach to those investors. This tool was developed over the span of eight months, with input from best-in-class founders and investors. This thesis documents the design and implementation of the tool, and evaluates its usage in production.

\section{A Study}

The data collected from VCWiz comprises the VCWiz Email Graph: a social-professional graph of founders, investors, their mutual connections, and the patterns of communication between all of them. This data is used in a study centered around FounderRank, a means of scoring founders based on the structure of the graph around them. The rankings generated by FounderRank educate investors on how to best use social relationships to evaluate a large set of founders who are being considered for a possible investment. Furthermore, these rankings demonstrate which social features of an individual are most crucial to successfully raising venture money.
